### 2025-02-06 paper/sections/other/constraints.qmd
ok that trick works

# Data:
# constraints = ["none", "both"]        # x1 cannot be mutated
constraints = ["both", "both"]        # x2 cannot be mutated
data = LinearlySeparable(
    n_train=500,
    batchsize=50,
    mutability=constraints
)
ce_data = get_ce_data(data)
val_size = data.n_validation / (data.n_validation + data.n_train)
train_set, val_set, _ = train_val_split(data, ce_data, val_size)

@@

```{julia}
obj = EnergyDifferentialObjective(lambda=[1.0,0.1,0.0])
# obj = VanillaObjective()
generator = GenericGenerator()
opt_state = Flux.setup(Descent(), model)
```

@@

model, logs = counterfactual_training(
    obj,
    model,
    generator,
    train_set,
    opt_state;
    val_set = val_set,
    nepochs = 50,
    mutability = Symbol.(constraints)
)
```

@@

```{julia}
coeff = get_log_reg_params(model)
db = get_decision_boundary(coeff)
Plots.scatter(ce_data)
Plots.abline!(db.slope, db.intercept; lw=5, label="Dec. Boundary")
```

>>>>

# Data:
constraints = ["none", "both"]        # x1 cannot be mutated
# constraints = ["both", "none"]        # x2 cannot be mutated
data = LinearlySeparable(
    n_train=500,
    batchsize=50,
    mutability=constraints
)
ce_data = get_ce_data(data)
val_size = data.n_validation / (data.n_validation + data.n_train)
train_set, val_set, _ = train_val_split(data, ce_data, val_size)

@@

```{julia}
using CounterfactualExplanations.Convergence
obj = EnergyDifferentialObjective(lambda=[1.0,1.0,0.0])
# obj = VanillaObjective()
generator = GenericGenerator()
opt_state = Flux.setup(Descent(), model)
conv = MaxIterConvergence()
```

```{julia}
using CTExperiments: get_log_reg_params, get_decision_boundary

function plot_db(model, x)
    coeff = get_log_reg_params(model)
    db = get_decision_boundary(coeff)
    plt = Plots.scatter(ce_data)
    yhat = [argmax(y) for y in eachcol(model(x))]
    Plots.scatter!(x[1,:], x[2,:], label="Counterfactuals", ms=15, shape=:star, color=yhat)
    Plots.abline!(plt, db.slope, db.intercept; lw=5, label="Dec. Boundary")
    display(plt)
end
```

@@

model, logs = counterfactual_training(
    obj,
    model,
    generator,
    train_set,
    opt_state;
    val_set = val_set,
    nepochs = 50,
    mutability = Symbol.(constraints),
    callback = plot_db,
    nce=50,
    convergence=conv, 
)
```

@@

```{julia}
coeff = get_log_reg_params(model)
display(coeff)
db = get_decision_boundary(coeff)
Plots.scatter(ce_data)
Plots.abline!(db.slope, db.intercept; lw=5, label="Dec. Boundary")
```
